---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# NoBodySorrow package

<!-- badges: start -->
<!-- badges: end -->

NoBodySorrow (nbs) is an R package with a range of functions to improve programming workflow in R.

## Installation

```{r, eval = F}
detach(package:nbs, unload=TRUE)
library(utils)
remove.packages("nbs")
devtools::install_github("mikeniemant/nbs")
```

# Load package
```{r}
library(nbs)
library(tidymodels)
ggplot2::theme_set(ggplot2::theme_bw())
```

# Dummy datasets
## single model tibble
```{r}
data(single_model_tibble)
single_model_tibble
```

## multi model tibble
```{r}
data(multi_model_tibble)
multi_model_tibble
```

# Functions
## computeBaseNetBenefit
```{r}
base_nbt <- computeBaseNetBenefit(single_model_tibble$y)
```

## computeNetBenefit
```{r}
nbt <- computeNetBenefit(pt = base_nbt$pt, 
                         y = single_model_tibble$y, 
                         pred = single_model_tibble$pred)

nbt <- base_nbt %>% # TODO: should be the original data frame
  left_join(nbt,
            by = "pt")

ggplot(nbt %>% 
         pivot_longer(cols = -pt, names_to = "model", values_to = "nbt") %>% 
         filter(nbt >= -0.1),
       aes(x = pt, y = nbt, colour = model, linetype = model)) + 
  geom_line() +
  labs(x = "Threshold probability (%)",
       y = "Net benefit",
       colour = "Model",
       linetype = "Model")
```

## computeCalibration
```{r}
computeCalibration(labs = single_model_tibble$y, preds = single_model_tibble$pred, event_level = "1")
```

## plotCalibration
```{r}
dat <- multi_model_tibble %>% 
  nest(dat = c(y, pred)) %>% 
  mutate(cal = map(dat, ~ computeCalibration(labs = .x$y,
                                             preds = .x$pred,
                                             event_level = "1",
                                             plot = F)))

# Plot calibration curve for all models
plotCalibration(dat %>% 
                  unnest(cal), 
                group = "model")
```
TODO:
- Set alpha geom_smooth

## plotPrc
```{r}
dat <- multi_model_tibble %>% 
  nest(dat = c(y, pred)) %>% 
  mutate(pr = map(dat, ~ .x %>% pr_curve(pred, truth = y, event_level = "second"))) %>% 
  unnest(pr)
plotPrc(dat, group = "model")
```

## plotRoc
```{r}
dat <- multi_model_tibble %>% 
  nest(dat = c(y, pred)) %>% 
  mutate(roc = map(dat, ~ .x %>% roc_curve(pred, truth = y, event_level = "second"))) %>% 
  unnest(roc)
plotRoc(dat, group = "model")
```

## cws
Clear work space
  - Remove all objects in environment
  - (Close any SQL connections)
  - (Close all clusters)

## findTodo
Find all `#TODO` statements in all .R and .Rmd files in a directory.

## replacePattern
Finds and replaces a  particular pattern in all .R and .Rmd files in a directory.

# Notes
Open a new issue [here](https://github.com/mikeniemant/nbs/issues) for any bug reports or feature requests.

Copyright (C) Michael Niemantsverdriet, the Netherlands, 2022, all rights reserved. Use for personal and educational purposes.
